\documentclass{beamer}

\mode<presentation> {
	
	\usetheme{Boadilla}
	\usecolortheme{seagull}  %plain
}
\usepackage{hyperref}
\usepackage{listings}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title[Django Workshop]{Django Workshop Session 2} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Advanced Programming} % Your name
\institute[AUT] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
	Amirkabir University of Technology\\ % Your institution for the title page
	\medskip
	\textit{} % Your email address
}
\date{Spring 2019} % Date, can be changed to a custom date

\begin{document}
	
	\begin{frame}
	\titlepage % Print the title page as the first slide
\end{frame}

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

%	PRESENTATION SLIDES

\section{Project 1 intro}
\begin{frame}
\frametitle{Blog project}
\begin{itemize}
\item In this project we will create a blog.
\item This is the first step to build a social network application.
\item The second project will have a lot in common with this Project.
\item The blog will be multi-user.
\end{itemize}
\end{frame}

\subsection{pages}
\begin{frame}
\frametitle{Pages}
\begin{itemize}
\item A home page with list of posts.
\item An about page.
\item A page for creating new posts.
\item A page containing drafts.
\item A user login page.
\end{itemize}
\end{frame}

\subsection{features}
\begin{frame}
\frametitle{features}
\begin{itemize}
\item Editable text input.
\item Editable posts contents.
\item Comments by viewers.
\item Confirm or delete comments by author.
\item Using stylesheets.
\item Links to other web sites.
\end{itemize}
\end{frame}

\section{Part 1}
\begin{frame}
\frametitle{Part 1}
\begin{itemize}
\item Create django project.
\item Add apps and initial run.
\item Set up essential files.
\end{itemize}
\end{frame}

\section{Part 2}
\begin{frame}
\frametitle{Part 2}
\begin{itemize}
\item Set up models.
\item import libraries.

\end{itemize}
\end{frame}

\section{Part 3}
\begin{frame}
\frametitle{Part 3}
\begin{itemize}
\item Set up forms.
\item Style widgets using Meta.

\end{itemize}
\end{frame}

\section{Part 4}
\begin{frame}[fragile]
\frametitle{Part 4}
\begin{itemize}
\item Create views and templates.
\item Connect them to urls.
\item Start using Class Based Views.
\item \href{https://docs.djangoproject.com/en/2.1/ref/models/querysets/#id4}{Field Lookups doc.}
\end{itemize}

\end{frame}

\section{Part 5}
\begin{frame}
\frametitle{Part 5}
\begin{itemize}
\item Complete templates.
\item Create Function Based Views.

\end{itemize}
\end{frame}


\section{Part 6}
\begin{frame}
\frametitle{Part 6}
\begin{itemize}
\item Create simple authentication system.

\end{itemize}
\end{frame}

\section{Part 7}
\begin{frame}[fragile]
\frametitle{Part 7}
\begin{itemize}
\item Review templates.
\item
\href{https://getbootstrap.com/docs/3.3/getting-started/}{Bootstrap 3}

\item
\href{https://github.com/yabwe/medium-editor}{Medium-editor}

\item
\href{https://codepen.io/thapliyalshivam/pen/dvgXVO}{Colorful css}
\item Google fonts
\end{itemize}
\end{frame}


\section{Ajax}
\begin{frame}[fragile]
\frametitle{Ajax}
\begin{itemize}
\item A for asynchronous.
\item JSON
\item jQuery
\item
\href{https://simpleisbetterthancomplex.com/tutorial/2016/08/29/how-to-work-with-ajax-request-with-django.html}{Example}

\end{itemize}
\end{frame}

%\begin{frame}[fragile]
%\frametitle{How to Create a Venv}
%\lstset{language=Bash}         
%\begin{lstlisting}[frame=single]
%$ cd <project directory>
%$ virtualenv -p <address of python> <name>
%$ source ./<name>/bin/activate
%$ pip install <packages>
%$ pip freeze -l > requirements.txt **
%$ ...
%$ deactivate
%\end{lstlisting}
%it is also possible to use IDE tools related to virtual environments.
%\\ ** We can also create requirements.txt file manually in order to avoid excess package installations.
%\end{frame}


\begin{frame}
\Huge \centering The End
\end{frame}

\end{document} 